Simple and robust inference of connectomes using partial correlation coefficients

### 2014-06-11 article.tex
wording

Note that our parameter tuning was mainly on \textit{normal-1} dataset and
partly on \textit{normal-4} dataset, therefore it may justify why these
networks are better retrieved despite the fact that some might be simpler to
infer.

>>>>

Note that our parameter tuning was mainly done on the \textit{normal-1} dataset
and partly on \textit{normal-4} dataset, therefore it may justify why these
networks are better retrieved despite the fact that some might be simpler to
infer.
